\documentclass{article}
\pagenumbering{arabic}

\begin{document}
\title {BODA BODA ASSASINATIONS IN UGANDA}
\author{MASSANGANZIRA ISAAC N  . 15/U/7440/EVE . 215014739}
\maketitle
\section{Introduction}
\subsection{Background}
The rampant killings by boda boda assasinations have taken cause and big attention
as a security threat for the people of Uganda. To be specific, the people being killed 
in this kind of manner are people with big positions within the civil service sector which
include the police, lawyers among others. And in addition, religions like Islam have
highly been targeted and many killings have been recorded.

\subsection{ Problem Statement}
There are majorly basic reasons that could lead to such killings around Uganda. Most
of all, not to blame the government, or the police for less or no security, the growing 
technological updates within the country have led to increased insecurities and many
people are now able to track their victims and harm them. The use of sophisticated
machine guns and first riding boda bodas accompanied by trackers and betrayal can 
only lead to death threats.
However, other problems include, certified anger amongst nationals which may also be
a result of corruption and greed where many deals have gone wrong, many betrayals
have encompassed and disagreements on money, property and power have caused 
bigger issues.


\section{Significance of the Study}
This study may be able to benefit a wider number of people which include firstly the 
general public as it will serve as a means of sensitization to the public so as to take 
on the recommended safety precautions and guidelines. Through sharing this knowledge,
one can draw personal measures towards misuse of boda boda and public awareness.
The government may also benefit through putting strict security measures and manpower
in the over sited areas.

\section{Scope of the Study}
This study was limited to the densely populated city of kampala and the sorrounding areas
where these killings have taken a great rise over the past 5years. This study was restricted
to only the well known previous cases in town which happened to have victimised top civil
servants like Maj. Mohammed Kiggundu who was shot down in Masanafu on 26th Nov 2016,
and the recent assasination of police spokesperson AIGP, Andrew Felix Kaweesi to mention
but a few as these have been covered by news agencies like NewVision, DailyMonitor.


\section {Methods of the Study}
Majorly to begin with, this research was based entirely on qualitative research analysis
which involved describing in detail specific situations using research tools like interviews,
surveys and observations. Qualitative research is primarily exploratory research, This 
will help to gain an understanding of underlying reasons ,opinions ans motivations while
providing insight sand help uncover trends in thought and dive deeper into the problem.
This research took place in kampala,Uganda since majority of these killings have been 
carried out in and around this town.


\section{Conclusion}
I conclude by saying all factors that cause oda boda assasinations have been included in
in this study. Although the few that have been mentioned have been by concrete evidence 
of examples.
Also all the effects have not been included due to failure to interview the concernedaffected 
parties to disclose more information aout the rising cause. 

\end{document}
